\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Full Stack Engineer}{Aug. 2025 -- Present}
      {Telus Digital}{Porto Alegre, RS, Brazil}
      \resumeItemListStart
        \resumeItem{Spearheaded the migration of a large-scale monolithic legacy system to a distributed microservices architecture using NestJS, decoupling services and improving deployment independence for a major enterprise hospitality client.}
        \resumeItem{Designed and delivered scalable, high-availability RESTful API backend services in NestJS and Node.js, enabling independent service scaling and improving long-term system maintainability across production environments.}
        \resumeItem{Architected and maintained automated CI/CD pipelines using GitHub Actions and AWS, accelerating release cadence and eliminating manual deployment bottlenecks.}
        \resumeItem{Implemented infrastructure-as-code (IaC) using Terraform and enforced cloud security compliance with Aquasec, reducing provisioning time and strengthening the overall application security posture.}
        \resumeItem{Monitored distributed system performance and reliability using Datadog, proactively identifying and resolving production bottlenecks to maintain high availability across environments.}
        \resumeItem{Conducted systematic code reviews and enforced software engineering best practices across the team, driving measurable improvements in code quality, test coverage, and long-term maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Software Engineer}{Aug. 2023 -- Aug. 2025}
      {DBC Company}{Porto Alegre, RS, Brazil}
      \resumeItemListStart
        \resumeItem{Architected and delivered multiple enterprise-grade microservice applications using Java, Spring Framework, Docker, and Kubernetes on Azure, supporting high-traffic production workloads.}
        \resumeItem{Built and deployed a scalable Content Management System (CMS) for a high-traffic e-commerce platform using Strapi.io, Node.js, and React.js, increasing content management efficiency and system maintainability by 80\%.}
        \resumeItem{Engineered high-throughput RESTful APIs using Java and Spring Framework integrated with Azure cloud services, handling thousands of concurrent daily requests with consistent sub-second response times.}
        \resumeItem{Developed full-stack web applications using TypeScript, Angular, and Spring Framework, delivering performant, accessible, and user-friendly software solutions across multiple client engagements.}
        \resumeItem{Partnered with cross-functional engineering teams to design and implement scalable Angular frontend architectures, accelerating feature delivery and improving collaboration efficiency.}
        \resumeItem{Established end-to-end (E2E) CI/CD pipeline integrations, automated unit, integration, and E2E test suites, and performed load and stress testing to ensure production reliability and deployment confidence.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Software Engineer}{Jul. 2020 -- Aug. 2023}
      {A.R. Phoenix}{Porto Alegre, RS, Brazil}
      \resumeItemListStart
        \resumeItem{Developed and maintained full-stack web applications using React.js and Next.js on the frontend and Spring Framework on the backend, delivering high-quality, scalable software products.}
        \resumeItem{Designed and scaled robust RESTful API backend services with Spring Boot, applying software development best practices around performance optimization, security hardening, and horizontal scalability.}
        \resumeItem{Integrated React.js frontend components with Spring Boot microservices, reducing inter-service latency and improving overall application throughput and system reliability.}
        \resumeItem{Championed code quality standards through systematic code reviews, refactoring initiatives, and adoption of SOLID principles, significantly reducing technical debt across the codebase.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Software Engineer}{Jan. 2017 -- Jul. 2020}
      {Freelance}{Porto Alegre, RS, Brazil}
      \resumeItemListStart
        \resumeItem{Designed and developed performant, accessible web and mobile applications using HTML5, CSS3, JavaScript, and TypeScript, delivering full-stack software development solutions across multiple industries.}
        \resumeItem{Optimized frontend performance through code profiling, asset optimization, and lazy loading strategies, achieving a 30\% reduction in page load time and improving Core Web Vitals scores.}
        \resumeItem{Integrated third-party payment gateway APIs into client e-commerce platforms, directly contributing to a 30\% increase in completed online transactions.}
        \resumeItem{Managed the full software development lifecycle --- from requirements gathering and architecture design to delivery and post-launch support --- ensuring on-time completion and consistent client satisfaction.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd